---
title: "Week 12: Review"
---

```{r}
week <- 12
source(here::here("course_info.R"))
```

## What you will learn this week

* Review Assignment 1
* Announce winner of the forecasting competition
* Discuss exam

## Exercises (on your own or in tutorial)

Complete Exercises 1-7 from [Section 10.7 of the book](https://otexts.com/fpp3/dynamic-exercises.html).

## Exercise solutions

::: {.callout appearance="minimal"}
<i class="bi bi-download"></i> [Week 12 Tutorial Solution.html](Week12.html){download="Week 12 Tutorial Solution.html"}
:::

## Pre-seminar activities

Catch up on any exercises not yet done

```{r}
#| output: asis
show_slides(week)
```


## Post-class activities

* Do any exercises not yet finished.
* Complete past exams: [[2021](/exams/exam2021.pdf)] [[2022](/exams/exam2022.pdf)] [[2023](/exams/exam2023.pdf)]
* Exam solutions: [[2021](/exams/exam2021_solutions.pdf)] [[2022](/exams/exam2022_solutions.pdf)] [[2023](/exams/exam2023_solutions.pdf)]

* Re-read the textbook
* Listen again to all lectures


