---
title: "Week 12: Review"
---

```{r}
week <- 12
source(here::here("course_info.R"))
```

## What you will learn this week

* Review Assignment 1
* Announce winner of the forecasting competition
* Discuss exam

## Pre-class activities

Catch up on any exercises not yet done


```{r}
#| output: asis
show_slides(week)
# show_slides_ann(week)
# show_activity(week, show_solutions = FALSE)
```


## Tutorial exercises


::: {.callout-note}

## Tutorial Learning Objectives

**The key points to understand**

- dynamic regression = regression model + ARIMA errors
- the difference between regression errors and white-noise innovations
- how to expand the model formula using lag/backshift notation
- how to form forecast equations by replacing future errors with zero and future values with forecasts 

:::


rev
-   Complete Q2 and Q7 from Tutorial 11 and Q16 from Tutorial 8. 




<!-- # ```{r} -->
<!-- # #| output: asis -->
<!-- # show_slides(week) -->
<!-- # ``` -->


<!-- ## Post-class activities -->

<!-- * Do any exercises not yet finished. -->
<!-- * Complete past exams: [[2023](exams/Exam2023.pdf)] [[2024](exams/Exam2024.pdf)] -->
<!-- <!-- * Exam solutions: [[2022](exams/Exam2022_solutions.pdf)][[2023](exams/Exam2023_solutions.pdf)][[2024](exams/Exam2024_solutions.pdf)] --> 


<!-- * Re-read the textbook -->
<!-- * Listen again to all lectures -->

## Past exams

* [[2023](exams/Exam2023.pdf)] [[2024](exams/Exam2024.pdf)][[2025](exams/Exam2025.pdf)]  

<!-- * Exam solutions: [[2023](exams/Exam2023_solutions.pdf)][[2024](exams/Exam2024_solutions.pdf)][[2025](exams/Exam2025_solutions.pdf)] -->

```{r, echo=FALSE}
#| output: asis
show_assignments(week)
```
