---
title: "Week 11: Dynamic regression"
---

```{r}
week <- 11
source(here::here("course_info.R"))
```

## What you will learn this week

* How to combine regression models with ARIMA models to form dynamic regression models
* Dynamic harmonic regression to handle complex seasonality
* Lagged predictors


## Pre-class activities

Read [Chapter 10 of the textbook](https://otexts.com/fpp3/dynamic.html) and watch all embedded videos


```{r}
#| output: asis
show_slides(week)
#show_slides_ann(week)
show_activity(week, show_solutions = FALSE)
```

## Seminar Code

::: {.callout appearance="minimal"}
<!-- <i class="bi bi-download"></i> [week4-code-incomplete.R](week4-code-incomplete.R){download="week4-code-incomplete.R"} -->
<i class="bi bi-download"></i> [week11-code.R](week11-code.R){download="week11-code.R"}
:::


## Tutorial exercises

::: {.callout-note}

## Tutorial Learning Objectives

1. **Fit dynamic regression with `ARIMA()`**.  
    - Able to specify and fit a regression model with ARIMA errors
    - Able to assess model fit using standard regression diagnostics and ARIMA residual diagnostics; and to use the fitted model to forecast when future predictor values are known.

2. **Evaluate and interpret dynamic regression**.  
    - Able to compare competing specifications using standard criteria; 
    - Able to interpret output from joint regression-and-error models
    - Able to discuss strengths and limitations of the forecasts and the prediction intervals.

:::

-   Complete Exercises 1, 2, 4, 5, 6, and 7 from [Section 10.7 of the book](https://otexts.com/fpp3/dynamic-exercises.html).

-   <i class="bi bi-download"></i> [Week 11 Tutorial Solution.html](Tutorial11Solution.html){download="Tutorial11Solution.html"}


<!-- ```{r} -->
<!-- #| output: asis -->
<!-- show_slides(week) -->
<!-- ``` -->

<!-- ## Seminar activities -->

<!-- ```{r} -->
<!-- #| child: activities.md -->
<!-- ``` -->


<!-- ## Seminar code -->

<!-- ::: {.callout appearance="minimal"} -->
<!-- <i class="bi bi-download"></i> [week11.R](week11.R){download="week11.R"} -->
<!-- ::: -->



```{r, echo=FALSE}
#| output: asis
show_assignments(week)
```
