---
title: "Week 11: Dynamic regression"
---

```{r}
week <- 11
source(here::here("course_info.R"))
```

## What you will learn this week

* How to combine regression models with ARIMA models to form dynamic regression models
* Dynamic harmonic regression to handle complex seasonality
* Lagged predictors

## Exercises (on your own or in tutorial)

Complete Exercises 1-7 from [Section 7.10 of the book](https://otexts.com/fpp3/regression-exercises.html).

## Exercise solutions

::: {.callout appearance="minimal"}
<i class="bi bi-download"></i> [Week 11 Tutorial Solution.html](Week11.html){download="Week 11 Tutorial Solution.html"}
:::

## Pre-class seminar

Read [Chapter 10 of the textbook](https://otexts.com/fpp3/dynamic.html) and watch all embedded videos


```{r}
#| output: asis
show_slides(week)
```

## Seminar activities

```{r}
#| child: activities.md
```


## Seminar code

::: {.callout appearance="minimal"}
<i class="bi bi-download"></i> [Seminar_code_week11.R](Seminar_code_week11.R){download="Seminar_code_week11.R"}
:::



```{r, echo=FALSE}
#| output: asis
show_assignments(week)
```
