---
title: "Week 6: Exponential smoothing"
---

```{r}
week <- 6
source(here::here("course_info.R"))
```

## What you will learn this week

* Exponential smoothing methods with trend and seasonality
* ETS models
* Automatic model selection using the AICc

## Pre-class activities

Read [Sections 8.3-8.7 of the textbook](https://otexts.com/fpp3/expsmooth.html) and watch all embedded videos.

```{r}
#| output: asis
#show_slides(week)
show_slides_ann(week)
show_activity(week, show_solutions = FALSE)
```

## Seminar Code

::: {.callout appearance="minimal"}
<!-- <i class="bi bi-download"></i> [week4-code-incomplete.R](week4-code-incomplete.R){download="week4-code-incomplete.R"} -->
<i class="bi bi-download"></i> [week6-code.R](week6-code.R){download="week6-code.R"}
:::


## Tutorial exercises 

::: {.callout-note}

## Tutorial Learning Objectives

1. **Compare alternative ETS model structures**. 
     - Select and fit different ETS models (e.g., ETS(A,N,N) vs ETS(A,A,N)). 
     - Evaluate and compare their fit (e.g., RMSE). 
     - Interpret forecast differences and prediction intervals, and justify model choice based on empirical performance.
     
2. **Select and justify appropriate ETS models for seasonal data**. 
     - Able to identify when multiplicative seasonality (and optional damped trend) is necessary.
     
3. **Compare multiple forecasting methods using training/test splits and cross-validation**. 
     - Use training/test sets and cross-validation to fit and compare a range of methods (ETS, transformed ETS, seasonal naïve, STL + ETS).

4. **Evaluate ETS method and identify its limitations**. 
    - Apply ETS model, assess forecasting quality, and recognise cases where ETS may not perform well and explain why.
    
:::


-   Complete Exercises 5, 7, 11, 14 from [Section 8.8 of the book](https://otexts.com/fpp3/expsmooth-exercises.html).

<!-- -   <i class="bi bi-download"></i> [Week 6 Tutorial Solution.html](Week6.html){download="Week 6 Tutorial Solution.html"} -->



```{r, echo=FALSE}
#| output: asis
show_assignments(week)
```
