---
title: "Week 1: What is forecasting?"
---

```{r}
week <- 1
source(here::here("course_info.R"))
```

## What you will learn this week

* How to think about forecasting from a statistical perspective
* What makes something easy or hard to forecast?
* Using the `tsibble` package in R

## Pre-class activities

- Before we start classes, make sure you are familiar with R, RStudio and the tidyverse packages. If you've already done one of ETX2250/ETC1010 or something equivalent you should be fairly familiar with these concepts and probably will not need much help. If you're new to R and the tidyverse, then you will need to get yourself up-to-speed. Work through the first five modules of the **StartR** tutorial at [startr.numbat.space](https://startr.numbat.space). Do as much of it as you think you need. For those students new to R, it is strongly recommended that you do all five modules. For those who have previously used R, concentrate on the parts where you feel you are weakest.

- Read the Appendix in the text book ([https://otexts.com/fpp3/appendix-using-r.html](https://otexts.com/fpp3/appendix-using-r.html)) and follow instructions to install R and RStudio on your personal computer. 

* Read [Chapter 1 of the textbook](http://OTexts.com/fpp3/intro.html) and watch all embedded videos. Pay particular attention to [Section 1.7](https://otexts.com/fpp3/perspective.html).

* Read [Section 2.1 of the textbook](https://otexts.com/fpp3/tsibbles.html#tsibbles) and watch the embedded video.


```{r}
#| output: asis

# show_slides(week)
show_activity(week, show_solutions = FALSE)
```


<!-- ## Seminar code -->

<!-- ::: {.callout appearance="minimal"} -->
<!-- <i class="bi bi-download"></i> [Seminar_code_week1.R](Seminar_code_week1.R){download="Seminar_code_week1.R"} -->
<!-- ::: -->


## Tutorial exercises

The main tasks for Week 1 tutorials will be:

1. To ensure that you have successfully installed R and RStudio on your own laptop.
2. Work your way through Chapters 1-5 [startr.numbat.space](https://startr.numbat.space). This is material we have prepared for you and other Monash students working in R. You should do these at your own pace to understand the concepts.

Your tutors will be in your tutorial class to assist you. 

<!-- [**Check your understanding quiz**](https://learning.monash.edu/mod/quiz/view.php?id=2327331) -->

```{r}
#| output: asis
show_assignments(week)
```
