---
title: "Week 1: What is forecasting?"
---

```{r}
week <- 1
source(here::here("course_info.R"))
```

## What you will learn this week

* How to think about forecasting from a statistical perspective
* What makes something easy or hard to forecast?
* Using the `tsibble` package in R

## Exercises (on your own or in tutorial)

Your task this week is to make sure you are familiar with R, RStudio and the tidyverse packages. If you've already done one of ETX2250/ETC1010 or something equivalent you should be fairly familiar with these concepts and probably will not need much help. But if you're new to R and the tidyverse, then you will need to get yourself up-to-speed. 

- To get started first look through the Appendix in the [textbook](https://otexts.com/fpp3/appendix-using-r.html).

- During the tutorials you will work your way through chapters 1-5 and 8 of [learnr.numbat.space](https://learnr.numbat.space/). This is material we have prepared for you and other Monash students working in R. 

- There are lots of online resources available to help you cover the necessary material. Here are my suggestions:

  - Read the first four chapters of ["ModernDive"](https://moderndive.netlify.app/).  
  - Work through the ["RYouWithMe"](https://rladiessydney.org/courses/ryouwithme/) course.
  
- You don't need to do everything in these links, but work on the parts where you are weakest. If you spend about 3-4 hours on this, you should cover enough of the relevant background to be ready for the rest of the unit.

Your tutors will be in your tutorial class to assist you should you need it but you should do these at your own pace to understand the concepts.

## Pre-class activities

* Install R and RStudio on your personal computer. Instructions are provided at [https://otexts.com/fpp3/appendix-using-r.html](https://otexts.com/fpp3/appendix-using-r.html).
* Read [Chapter 1 of the textbook](http://OTexts.com/fpp3/intro.html) and watch all embedded videos.
* Read [Section 2.1 of the textbook](https://otexts.com/fpp3/tsibbles.html#tsibbles) and watch the embedded video.


```{r}
#| output: asis
show_slides(week)
show_activity(week)
```


## Seminar code

::: {.callout appearance="minimal"}
<i class="bi bi-download"></i> [Seminar_code_week1.R](Seminar_code_week1.R){download="Seminar_code_week1.R"}
:::


```{r}
#| output: asis
show_assignments(week)
```
