---
title: "Week 9: ARIMA models"
---

```{r}
week <- 9
source(here::here("course_info.R"))
```

## What you will learn this week

* Seasonal ARIMA models
* Computing forecasts for ARIMA models
* ARIMA vs ETS models

## Exercises (on your own or in tutorial)

Complete Exercises 6-8, 15-16 from [Section 9.11 of the book](https://otexts.com/fpp3/arima-exercises.html).


## Exercise solutions

<!-- ::: {.callout appearance="minimal"} -->
<!-- <i class="bi bi-download"></i> [Week 9 Tutorial Solution.html](Week9.html){download="Week 9 Tutorial Solution.html"} -->
<!-- ::: -->



## Pre-seminar activities

Read [Sections 9.8-9.10 of the textbook](https://otexts.com/fpp3/arima.html) and watch all embedded videos


```{r}
#| output: asis
show_slides(week)
```

## Seminar activities

```{r}
#| child: activities.md
```


## Seminar code

::: {.callout appearance="minimal"}
<i class="bi bi-download"></i> [Seminar_code_week9.R](Seminar_code_week9.R){download="Seminar_code_week9.R"}
:::



```{r, echo=FALSE}
#| output: asis
show_assignments(week)
```
