---
title: "Week 9: ARIMA models"
---

```{r}
week <- 9
source(here::here("course_info.R"))
```


## What you will learn this week

* Seasonal ARIMA models
* Computing forecasts for ARIMA models
* ARIMA vs ETS models

## Pre-class activities

Read [Sections 9.8-9.10 of the textbook](https://otexts.com/fpp3/arima.html) and watch all embedded videos


## Tutorial exercises

::: {.callout-note}

## Tutorial Learning Objectives

1. **Develop and evaluate seasonal ARIMA models**.   
    - Able to transform/difference seasonal series, fit and diagnose competing ARIMA models, and produce forecasts (including comparing against ETS and STL-adjusted approaches).

2. **Compute ARIMA-based forecasts manually**.     
    - Able to use a specified ARIMA model equation and estimated parameters to hand-calculate multi-step forecasts, then fit the same model in R and explain differences between manual and software forecasts.

:::

-   Complete Exercises 11, 12, 13, 15 (d,e), 16 (d,e)  from [Section 9.11 of the book](https://otexts.com/fpp3/arima-exercises.html).


<!-- -   <i class="bi bi-download"></i> [Week 9 Tutorial Solution.html](Tutorial9Solution.html){download="Week 9 Tutorial Solution.html"} -->


<!-- # ```{r} -->
<!-- # #| output: asis -->
<!-- # show_slides(week) -->
<!-- # ``` -->

<!-- ## Seminar activities -->

<!-- ```{r} -->
<!-- #| child: activities.md -->
<!-- ``` -->


<!-- ## Seminar code -->

<!-- ::: {.callout appearance="minimal"} -->
<!-- <i class="bi bi-download"></i> [week9.R](week9.R){download="week9.R"} -->
<!-- ::: -->



```{r, echo=FALSE}
#| output: asis
show_assignments(week)
```
