---
title: "Week 10: Multiple regression and forecasting"
---

```{r}
week <- 10
source(here::here("course_info.R"))
```

## What you will learn this week

* Useful predictors for time series forecasting using regression
* Selecting predictors
* Ex ante and ex post forecasting

## Pre-class activities

Read [Chapter 7 of the textbook](https://otexts.com/fpp3/regression.html) and watch all embedded videos



```{r}
#| output: asis
#show_slides(week)
show_slides_ann(week)
show_activity(week, show_solutions = FALSE)
```

## Seminar Code

::: {.callout appearance="minimal"}
<!-- <i class="bi bi-download"></i> [week4-code-incomplete.R](week4-code-incomplete.R){download="week4-code-incomplete.R"} -->
<i class="bi bi-download"></i> [week10-code.R](week10-code.R){download="week10-code.R"}
:::


## Tutorial exercises

::: {.callout-note}

## Tutorial Learning Objectives

1. **Fit and forecast with `TSLM()`**.  
    - Able to build linear time series regression models for forecasting. 
   - Understand how to use regression models for forecasting, including selecting predictors and evaluating forecasts.

2. **Evaluate regression forecasts**.  
    - Able to use residual diagnostics and information criteria to compare models. 
    - Able to interpret relationships on transformed scales where used. 
    - Able to write out the regression equation for a fitted model, including interpreting coefficients and using the equation to compute forecasts.

:::

-   Complete Exercises 1-7 from [Section 7.10 of the book](https://otexts.com/fpp3/regression-exercises.html).

-   <i class="bi bi-download"></i> [Week 10 Tutorial Solution.html](Tutorial10Solution.html){download="Week 10 Tutorial Solution.html"}




```{r, echo=FALSE}
#| output: asis
show_assignments(week)
```
