---
title: "Week 2: Time series graphics"
---

```{r}
#| cache: false
week <- 2
source(here::here("course_info.R"))
```

## What you will learn this week

* Different types of plots for time series including time plots, season plots, subseries plots, lag plots and ACF plots
* The difference between seasonal patterns and cyclic patterns in time series
* What is "white noise" and how to identify it.

## Exercises (on your own or in tutorial)

Complete Exercises 1-5 from [Section 2.10 of the book](https://otexts.com/fpp3/graphics-exercises.html).

## Exercise solutions

::: {.callout appearance="minimal"}
<i class="bi bi-download"></i> [Week 2 Tutorial Solution.html](Week2.html){download="Week 2 Tutorial Solution.html"}
:::


## Pre-seminar activities

Read [Chapter 2 of the textbook](https://otexts.com/fpp3/graphics.html) and watch all embedded videos

```{r}
#| output: asis
show_slides(week)
```

## Seminar activities

```{r}
#| child: activities.qmd
```


## Seminar code

::: {.callout appearance="minimal"}
<i class="bi bi-download"></i> [Seminar_code_week2_incomplete.R](Seminar_code_week2_incomplete.R){download="Seminar_code_week2_incomplete.R"}
:::



```{r, echo=FALSE}
#| output: asis

show_assignments(week)
```
