---
title: "ETF5231 Group Assignment 3"
subtitle: 'Group Number and Name'
author:
- Student Name (ID)
- Student Name (ID)
- Student Name (ID)
- Student Name (ID)

output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval=TRUE, error=TRUE, cache=TRUE)
# write the appropriate code to read in your group data from Group_Data.csv
```


## Question 1

*Plot your time series. By observing the plot and describing its components select an ETS model you think is appropriate for forecasting. Make sure you justify your choice (no more than 150 words). (8 marks)*

```{r}

```

\newpage
## Question 2

*Search for an ETS model for your series using appropriate information criteria. Describe the process you have implemented. Which part of the data is used in this process? Which model have you selected and why? Show all necessary output (12 marks)*

```{r}

```
\newpage
## Question 3

*Now use time series cross-validation to compare the model selected from the previous step, along with ETS(M,N,M), ETS(M,A,M) and ETS(M,Ad,M) models. You will need to think about more than h=1 step-ahead. Think about an appropriate range of forecast horizons and justify your choice. Fully describe the process you have implemented. Show all necessary output. (Hint the code at the end of this section [https://otexts.com/fpp3/tscv.html](https://otexts.com/fpp3/tscv.html) may help you to get started.) (22 marks)*

```{r}

```

\newpage
## Question 4

*Which model do you prefer for your data? Choose a model and explain your choice. Describe its components and estimated parameters and how these are appropriate for your data. Perform all the necessary diagnostic checks and comment. (max 200 words) (12 marks)*

```{r}

```

\newpage
## Question 5

*Generate forecasts for the two years following the end of your sample using your chosen/best model. Plot them and briefly comment on these. (No more than 100 words). (4 marks)*

```{r}

```