---
title: "Week 8: ARIMA models"
---

```{r}
week <- 8
source(here::here("course_info.R"))
```


## What you will learn this week

* AR, MA, ARMA and ARIMA models
* Selecting model orders manually and automatically

## Pre-class activities

Read [Sections 9.3-9.8 of the textbook](https://otexts.com/fpp3/arima.html) and watch all embedded videos


```{r}
#| output: asis
#show_slides(week)
show_slides_ann(week)
show_activity(week, show_solutions = FALSE)
```

## Seminar Code

::: {.callout appearance="minimal"}
<!-- <i class="bi bi-download"></i> [week4-code-incomplete.R](week4-code-incomplete.R){download="week4-code-incomplete.R"} -->
<i class="bi bi-download"></i> [week8-code.R](week8-code.R){download="week8-code.R"}
:::

## Tutorial exercises

::: {.callout-note}

## Tutorial Learning Objectives

1. **Fit and compare ARIMA forecasting models**. 
    - Able to use ARIMA() (with transformations where needed) to select an appropriate model, generate forecasts, and compare them against alternative specified ARIMA structures.

2. **Evaluate model adequacy using residual diagnostics**. 
    - Check whether ARIMA model residuals resemble white noise (including examining autocorrelation in residuals) and use this evidence to refine or justify model choice.

3. **Translate between model equations and ARIMA notation**. 
    - Recognise ARIMA model equations in algebraic form and correctly express them using ARIMA $(p,d,q)$ notation.

:::

-   Complete Exercises 7, 8, 15 (a to c), 16 (a to c) from [Section 9.11 of the book](https://otexts.com/fpp3/arima-exercises.html).

-   <i class="bi bi-download"></i> [Week 8 Tutorial Solution.html](Tutorial8Solution.html){download="Tutorial8Solution.html"}







<!-- ```{r} -->
<!-- #| output: asis -->
<!-- show_slides(week) -->
<!-- ``` -->

<!-- ## Seminar activities -->

<!-- ```{r} -->
<!-- #| child: activities.md -->
<!-- ``` -->


<!-- ## Seminar code -->

<!-- ::: {.callout appearance="minimal"} -->
<!-- <i class="bi bi-download"></i> [week8.R](week8.R){download="week8.R"} -->
<!-- ::: -->



```{r, echo=FALSE}
#| output: asis
show_assignments(week)
```
