---
title: "Week 8: ARIMA models"
---

```{r}
week <- 8
source(here::here("course_info.R"))
```

## What you will learn this week

* AR, MA, ARMA and ARIMA models
* Selecting model orders manually and automatically

## Exercises (on your own or in tutorial)

Complete Exercise 1-4 from [Section 9.11 of the book](https://otexts.com/fpp3/arima-exercises.html)

## Exercise solutions

::: {.callout appearance="minimal"}
<i class="bi bi-download"></i> [Week 8 Tutorial Solution.html](Week8.html){download="Week 8 Tutorial Solution.html"}
:::


## Pre-seminar activities

Read [Sections 9.3-9.8 of the textbook](https://otexts.com/fpp3/arima.html) and watch all embedded videos



```{r}
#| output: asis
show_slides(week)
```

## Seminar activities

```{r}
#| child: activities.md
```


## Seminar code

::: {.callout appearance="minimal"}
<i class="bi bi-download"></i> [Seminar_code_week8.R](Seminar_code_week8.R){download="Seminar_code_week8.R"}
:::



```{r, echo=FALSE}
#| output: asis
show_assignments(week)
```
