---
title: "Week 5: Exponential smoothing"
---

```{r}
week <- 5
source(here::here("course_info.R"))
```

## What you will learn this week

* Simple exponential smoothing and corresponding ETS models
* Methods with trend and corresponding ETS models
* ETS model notation

## Pre-class activities

Read [Sections 8.1-8.4 of the textbook](https://otexts.com/fpp3/expsmooth.html) and watch all embedded videos


```{r}
#| output: asis
#show_slides(week)
show_slides_ann(week)
show_activity(week, show_solutions = FALSE)
```

## Seminar Code

::: {.callout appearance="minimal"}
<!-- <i class="bi bi-download"></i> [week4-code-incomplete.R](week4-code-incomplete.R){download="week4-code-incomplete.R"} -->
<i class="bi bi-download"></i> [week5-code.R](week5-code.R){download="week5-code.R"}
:::


## Tutorial exercises

::: {.callout-note}

## Tutorial Learning Objectives

1. **Implement and interpret exponential smoothing models**. 
    - Able to estimate simple exponential smoothing (SES) model, interpret the smoothing parameters, and generate point and interval forecasts.

2. **Develop custom forecasting functions**.   
    - Write and test user-defined functions to perform simple exponential smoothing, compare their outputs with built-in functions (like ETS()), and understand the computational steps involved.

3. **Optimise model parameters using numerical methods**. 
    - Modify exponential smoothing functions to compute an error measure and use numerical optimisation methods to determine the optimal smoothing parameter
    - Able to compare results with the automatic ETS estimation.

:::

-   Complete Exercises 1-4 from [Section 8.8](https://otexts.com/fpp3/expsmooth-exercises.html).

-   <i class="bi bi-download"></i> [Week 5 Tutorial Solution.html](Tutorial5Solution.html){download="Tutorial5Solution.html"}



```{r, echo=FALSE}
#| output: asis

show_assignments(week)
```
