---
title: "ETF3231/5231 Individual Assignment 3"
author: "Your name and Student ID"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval=TRUE, error=TRUE, cache=TRUE)
library(fpp3)
```

For the tasks that follow you will be modelling the **original data without any transformations** performed (even if you previously deemed it necessary). For questions 1 to 5 use the training data, i.e., ignore the last two years of your data.

## Question 1

*Plot your time series. By observing the plot and describing its components select an ETS model you think is appropriate for forecasting. Make sure you justify your choice (no more than 150 words). (8 marks)*

```{r}

```

\newpage
## Question 2

*Estimate the ETS model you described in Question 1 and show the estimated model output. Describe and comment on the estimated parameters and components. Include any plots you see necessary (no more than 150 words). (14 marks)*

```{r}

```

\newpage
## Question 3

*Plot the residuals from the model and comment on these (no more than 50 words). Perform some diagnostic checks and comment on whether you are satisfied with the fit of the model. (Make sure you state all relevant information for any hypothesis test you perform such as the null hypothesis, the degrees of freedom, the decision, etc.). (10 marks)*

```{r}

```

\newpage
## Question 4

*Let R select an ETS model. What model has been chosen and how has this model been chosen? (No more than 100 words). (6 marks)*

```{r}

```

\newpage
## Question 5

*Comment on how the model chosen by R is different to the model you have specified (no more than 50 words). Which of the two models would you choose and why? (no more than 50 words). (Hint: think about model selection here but also check your residuals).* 

*If the models are identical specify a plausible alternative. Give a brief justification for your choice (no more than 100 words). (Hint: also check the residuals from this model).  (12 marks)*

```{r}

```

\newpage
## Question 6

*Generate forecasts for the last two years of your sample using both alternative ETS models (you will need to re-estimate both models over the appropriate training sample). Plot the forecasts and forecast intervals. Briefly comment on these. Which model does best? (No more than 100 words). (8 marks)*

```{r}

```

\newpage
## Question 7

*Generate forecasts for the two years following the end of your sample using your chosen model. Plot them and briefly comment on these. (No more than 100 words).  (4 marks)*

```{r}

```

